Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-06-30 doc/manuscript/manuscript.Rmd
Move graph to main section; demote bargraph

![
Barplot showing abundance of each Mycelial Compatibility Group (MCG) in descending order.
Singletons (46) have been removed for clarity.
White bars represent sample counts and grey bars represent counts of unique multilocus genotypes (MLG).
The transparency associated with the grey bars represent the evenness of the distribution of the MLGs within a given MCG as shown in the inset histograms.
](../../results/figures/publication/Figure1Z.pdf){#barplot width=70%}

@@

The associations between MCGs and MLGs are complicated \@ref(biggraph)

@@

![
Graph showing associations between Mycelial Compatibility Groups dotted outline and Multilocus Genotypes full outline
](../../results/figures/publication/FigureS2.pdf){#biggraph width=100%}

\newpage

>>>>

![
Barplot showing abundance of each Mycelial Compatibility Group (MCG) in descending order.
Singletons (46) have been removed for clarity.
White bars represent sample counts and grey bars represent counts of unique multilocus genotypes (MLG).
The transparency associated with the grey bars represent the evenness of the distribution of the MLGs within a given MCG as shown in the inset histograms.
](../../results/figures/publication/Figure1Z.pdf){#barplot width=50%}

@@

The associations between MCGs and MLGs are complicated (Fig. \@ref(biggraph))

![
Graph showing complex associations between Mycelial Compatibility Groups (dotted nodes) and Multilocus Genotypes (full nodes). 
Node size reflect the number of samples represented by each node (circle).
Edges (arrows) point from Mycelial Compatibility Group to Multilocus Genotype where the weight (thickness) of the edge represents the number of samples shared.
Node color represents the community assignment based on the walktrap algorithm with a maximum of four steps [@pons2006computing].
](../../results/figures/publication/FigureS2.pdf){#biggraph width=100%}

@@
